Covid-19 A Spatio-Temporal Investigation.

### 2021-01-09 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 To evaluate the spatial association during the pandemic, the knn method was used to create spatial polygons and to build the spatial weight matrices, necessary to calculate the Global Moran's I and the *LISA*. The Global Moran's I is widely used and gathers all spatial dependence in one value $\!\!^6$, while the Local Moran's I useful to identify patterns of spatial association, is of great value

 , se faz útil pois de acordo com Maia, Gomes e Almeida (2018, p.930) enquanto o índice de Moran global pode sugerir que haja baixa correlação espacial nos dados, os valores do *LISA* podem identificar sub-regiões geográficas em que o agrupamento (*clustering*) negativo ou positivo ocorram $\!\!^7$.

>>>>

 To evaluate spatial association during the pandemic, a knn method was used to create spatial polygons and to build spatial weight matrices, which are necessary to calculate the Global Moran's I and the *LISA*. The Global Moran's I is widely used and gathers all spatial dependence in one value $\!\!^6$, while the use of the Local Moran's I is important to identify patterns of spatial association, hence the *LISA* should be used with the Global Moran's I, as it's stated by Maia, Gomes and Almeida (2019, p.930) "while the global Moran's I may suggest, in general, that there is little spatial autocorrelation in the data, LISA values can identify smaller geographic areas where positive or negative clustering occurs." $\!\!^7$.
